Hydrodynamics and rheology of adhesive vesicle doublets

### 2019-02-07 vesicle_code/docs/adhesion/adhesion.tex
small changes as discussed with Yuan on skype

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Adhesion Model}
Sukumaran and Seifert~\cite{suk-sei2001} consider adhesion between a
single three-dimensional vesicle and a solid wall at $z=0$.  They use
the adhesion potential of the function form
\begin{align}
\label{eq:adhesion_potential}
  \phi(z) = H \left[ 
    \left(\frac{\delta}{z}\right)^m - \frac{m}{n} \left(\frac{\delta}{z}\right)^n \right],
\end{align}
where $z$ is the distance between the solid wall and the vesicle,
$\mathcal{H}$ is the Hamaker constant, $\delta$ is the adhesion length
scale, and $(m,n) = (4,2)$.  We generalize this model to an unbounded
suspension of vesicles. We assume that the adhesion force applies
between all pairs of points on different vesicles, so we are interested
in Hamaker constants that are appropriate for lipid-lipid interactions.
We use Hamaker constants ranging from $0.1$ to $1$ times the bending
rigidity modulus.  In Appendix~\ref{sec:appendixA}, the adhesive force
at a point $\xx$ on vesicle $j$ is shown to be
\begin{align}
  \AA\xx:=-\mathcal{H} m \delta^{n}\sum_{\substack{k=1 \\ k \neq j}}^M 
  \int_{\gamma_k} \frac{\xx - \yy}{\|\xx - \yy\|^{m+2}} 
  \left(\delta^{m-n} - \|\xx - \yy\|^{m-n} \right) ds_\yy.
  \label{eqn:adhesionForce}
\end{align}
The adhesion model is illustrated in Figure~\ref{fig:adhesionModel}.

@@

Finally, we investigate the rheology of a suspension of a doublet by
computing the effective viscosity of a doublet and compare it to the
effective viscosity of a single tank-treading vesicle. The effective
viscosity is defined as the viscosity of a homogeneous Newtonian fluid
with the same energy dissipation per macroscopic element of fluid.  In a
simple shear flow, the intrinsic viscosity, $[\mu]$ is
\begin{align*}
  [\mu]:= \frac{\mu_{\mathrm{eff}} - \mu_0}{\phi \mu_0} = 
  \frac{1}{\chi \mu_0 T} \int_{T_i}^{T_e} 
  \langle \sigma_{12} \rangle dt,
\end{align*}
where
\begin{align*}
  \langle \tau \rangle = \frac{1}{|\omega|} \int_{\gamma}
    \xxi \otimes \xx ds,
\end{align*}
where $\phi$ is the area fraction of vesicles, $/tau$ is the stress due
to the vesicles, and $\langle \cdot \rangle$ is the spatial average.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Adhesion Model}
Sukumaran and Seifert~\cite{suk-sei2001} consider adhesion between a
single three-dimensional vesicle and a solid wall at $z=0$.  They use
the adhesion potential of the function form
\begin{align}
\label{eq:adhesion_potential}
  \phi(z) = H \left[ 
    \left(\frac{\delta}{z}\right)^m - \frac{m}{n} \left(\frac{\delta}{z}\right)^n \right],
\end{align}
where $z$ is the distance between the solid wall and the vesicle,
$\mathcal{H}$ is the Hamaker constant, $\delta$ is the adhesion length
scale, and $(m,n) = (4,2)$.  We generalize this model to an unbounded
suspension of vesicles. We assume that the adhesion force applies
between all pairs of points on different vesicles, so we are interested
in Hamaker constants that are appropriate for lipid-lipid interactions.
We use Hamaker constants ranging from $\mathcal{O}(10^{-1})$ to
$\mathcal{O}(10^0)$ times the bending rigidity modulus.  In
Appendix~\ref{sec:appendixA}, the adhesive force at a point $\xx$ on
vesicle $j$ is shown to be
\begin{align}
  \AA\xx:=-\mathcal{H} m \delta^{n}\sum_{\substack{k=1 \\ k \neq j}}^M 
  \int_{\gamma_k} \frac{\xx - \yy}{\|\xx - \yy\|^{m+2}} 
  \left(\delta^{m-n} - \|\xx - \yy\|^{m-n} \right) ds_\yy.
  \label{eqn:adhesionForce}
\end{align}
The adhesion model is illustrated in Figure~\ref{fig:adhesionModel}.

@@

Finally, we investigate the rheology of a suspension of a doublet by
computing the effective viscosity of a doublet and compare it to the
effective viscosity of a single tank-treading vesicle. The effective
viscosity is defined as the viscosity of a homogeneous Newtonian fluid
with the same energy dissipation per macroscopic element of fluid.  In a
simple shear flow, the intrinsic viscosity, $[\mu]$ is
\begin{align*}
  [\mu]:= \frac{\mu_{\mathrm{eff}} - \mu_0}{\phi \mu_0} = 
  \frac{1}{\chi \mu_0 T} \int_{T_i}^{T_e} 
  \langle \sigma_{12} \rangle dt,
\end{align*}
where
\begin{align*}
  \langle \tau \rangle = \frac{1}{|\omega|} \int_{\gamma}
    \xxi \otimes \xx ds,
\end{align*}
where $\phi$ is the area fraction of vesicles, $\tau$ is the stress due
to the vesicles, and $\langle \cdot \rangle$ is the spatial average.
